Summary of models

### 2022-09-27 Rmd/Models.Rmd
added plots

@@

@@

@@

#Models _ fruit proportion 
# hymenoptera visitation
ta_f4<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

@@

ta_f4<-ta_f4 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f4<-filter(ta_f4, !term == "sd__(Intercept)")

ta_f4 %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

>>>>

## general correlation 
```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
# replace NAs by 0
# hay especies de plantas que presentan datos de fruit y seed pero no de polinizador (durante el tiempo observado no se ve ningun polinizador )
Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))

cor_general<-Pollinator_Plant %>% 
  select(fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)

corr <- round(cor(cor_general), 4)

corr %>% 
    kable("latex",booktabs = TRUE,linesep = "")

```{r,,echo=FALSE, warning=FALSE,message=FALSE, out.width="89%"}
ggcorrplot(corr, hc.order = TRUE, type = "lower",
           lab = TRUE)
```

@@

visitation rate is calculated like frequency/ flower abundance

@@

Hymenoptera visitation is calculated like hymenoptera frequency / Flower abundance
```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_fruitproportion_3 <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=Hym_visit, y=fruit_proportion) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_fruitproportion_3[[1]],plots_fruitproportion_3[[2]],plots_fruitproportion_3[[3]],plots_fruitproportion_3[[4]],plots_fruitproportion_3[[5]],plots_fruitproportion_3[[6]],plots_fruitproportion_3[[7]],plots_fruitproportion_3[[8]],plots_fruitproportion_3[[9]],plots_fruitproportion_3[[10]],plots_fruitproportion_3[[11]],plots_fruitproportion_3[[12]], ncol=3, nrow=4)

Summary of models for fruit proportion ~ Hymenoptera visitation per plant species. Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed. Site_ID as factor random
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

#Models _ fruit proportion 
# hymenoptera visitation
mod_plots_fruitproportion_3<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_plots_fruitproportion_3<-mod_plots_fruitproportion_3 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_plots_fruitproportion_3<-filter(mod_plots_fruitproportion_3, !term == "sd__(Intercept)")

mod_plots_fruitproportion_3 %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_plots_fruitproportion_3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_fruitproportion_3_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion_3_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_fruitproportion.3 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=mod_fruitproportion.3$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2=mod_fruitproportion.3$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_fruitproportion.3$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=mod_fruitproportion.3$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=mod_fruitproportion.3$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=mod_fruitproportion.3$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7= mod_fruitproportion.3$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8=mod_fruitproportion.3$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9=mod_fruitproportion.3$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10=mod_fruitproportion.3$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11=mod_fruitproportion.3$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12=mod_fruitproportion.3$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

## Pollinator frequency

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_fruitproportion_4 <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=Frequency, y=fruit_proportion) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_fruitproportion_4[[1]],plots_fruitproportion_4[[2]],plots_fruitproportion_4[[3]],plots_fruitproportion_4[[4]],plots_fruitproportion_4[[5]],plots_fruitproportion_4[[6]],plots_fruitproportion_4[[7]],plots_fruitproportion_4[[8]],plots_fruitproportion_4[[9]],plots_fruitproportion_4[[10]],plots_fruitproportion_4[[11]],plots_fruitproportion_4[[12]], ncol=3, nrow=4)

Summary of models for fruit proportion ~ pollinator frequency per plant species. Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed. Site_ID as factor random
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

# frequency
mod_fruitproportion_4<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_fruitproportion_4<-mod_fruitproportion_4 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruitproportion_4<-filter(mod_fruitproportion_4, !term == "sd__(Intercept)")

mod_fruitproportion_4 %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_fruitproportion_4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_fruitproportion_4_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion_4_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_fruitproportion.4 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Frequency"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
 geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=mod_fruitproportion.4$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2=mod_fruitproportion.4$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_fruitproportion.4$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

P4=mod_fruitproportion.4$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=mod_fruitproportion.4$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=mod_fruitproportion.4$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=mod_fruitproportion.4$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8= mod_fruitproportion.4$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9=mod_fruitproportion.4$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10=mod_fruitproportion.4$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11=mod_fruitproportion.4$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12=mod_fruitproportion.4$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Frequency, y = fruit_proportion),shape=20)+  labs(x = "Frequency",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

# Seed number

seed number is calculated like seed number mean per fruit in plant individual per plant species

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_seed <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=richness, y=Seeds) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_seed[[1]],plots_seed[[2]],plots_seed[[3]],plots_seed[[4]],plots_seed[[5]],plots_seed[[6]],plots_seed[[7]],plots_seed[[8]],plots_seed[[9]],plots_seed[[10]],plots_seed[[11]],plots_seed[[12]], ncol=3, nrow=4)

Summary of models for seed numbers ~ richness per plant species (LMM). Site_ID as factor random

@@

#Models _ Seed numbers 
# richness
mod_seed<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

@@

mod_seed<-mod_seed %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed<-filter(mod_seed, !term == "sd__(Intercept)" & !term =="sd__Observation")

mod_seed %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_seed_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_seed_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_seed.1 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "richness"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
 geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=mod_seed.1$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2=mod_seed.1$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_seed.1$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=mod_seed.1$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=mod_seed.1$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=mod_seed.1$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=mod_seed.1$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8=mod_seed.1$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9=mod_seed.1$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10=mod_seed.1$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11=mod_seed.1$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12=mod_seed.1$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_seed_2 <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=visitatio_rate, y=Seeds) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_seed_2[[1]],plots_seed_2[[2]],plots_seed_2[[3]],plots_seed_2[[4]],plots_seed_2[[5]],plots_seed_2[[6]],plots_seed_2[[7]],plots_seed_2[[8]],plots_seed_2[[9]],plots_seed_2[[10]],plots_seed_2[[11]],plots_seed_2[[12]], ncol=3,nrow=4)

Summary of models for seed number ~ visitation rate per plant species (LMM). Site_ID as factor random

# visitation rate
mod_seed2<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_seed2<-mod_seed2 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed2<-filter(mod_seed2, !term == "sd__(Intercept)" & !term =="sd__Observation")

mod_seed2 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")
```

mod_seed2_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_seed2_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_seed.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "visitatio_rate")))  %>%  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=mod_seed.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2=mod_seed.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_seed.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=mod_seed.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=mod_seed.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=mod_seed.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=mod_seed.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8=mod_seed.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  visitatio_rate, y = Seeds),shape=20)+labs(x = "visitation_rate",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9=mod_seed.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  visitatio_rate, y = Seeds),shape=20)+labs(x = "visitation_rate",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10=mod_seed.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11= mod_seed.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12=mod_seed.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_seed_3 <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=Hym_visit, y=Seeds) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_seed_3[[1]],plots_seed_3[[2]],plots_seed_3[[3]],plots_seed_3[[4]],plots_seed_3[[5]],plots_seed_3[[6]],plots_seed_3[[7]],plots_seed_3[[8]],plots_seed_3[[9]],plots_seed_3[[10]],plots_seed_3[[11]],plots_seed_3[[12]], ncol=3,nrow=4)

Summary of models for seed number ~ Hymenoptera visitation per plant species (LMM). Site_ID as factor random

# hymenoptera visitation
mod_seed3<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_seed3<-mod_seed3 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed3<-filter(mod_seed3, !term == "sd__(Intercept)" & !term =="sd__Observation")

mod_seed3 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_seed3_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_seed3_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_seed.3 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=mod_seed.3$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit, y = Seeds),shape=20)+  labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2=mod_seed.3$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_seed.3$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=mod_seed.3$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=mod_seed.3$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
